An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-04-12 poly-embed-journal/poly-embed-journal.tex
Adding thoughts on what to do with section 5

\begin{definition}
  \raft{For Bo: added this def, changed def embedding}
  Let $L:\R\to\reals^\Y_+$ be a generic loss.
  We say $\Sc \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
  We further say $\Sc$ is \emph{minimally representative} or a \emph{minimal representative set} if it has the smallest cardinality among all representative sets.
\end{definition}

\begin{definition}[Embedding a loss]\label{def:loss-embed}
  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ over a set $\Sc$ if there exists some injective embedding $\varphi:\Sc\to\reals^d$ such that
  (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
  % \begin{equation}\label{eq:embed-loss}
  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
  % \end{equation}
  \begin{equation}\label{eq:embed-loss}
    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
  \end{equation}
  We simply say $L$ \emph{embeds} $\ell$ if there is some representative set $\Sc$ such that $L$ embeds $\ell$ over $\Sc$.
\end{definition}

@@

\raf{Some thoughts on this section:
  \begin{itemize}
  \item It's unclear to me how much of the properties stuff is for funzies versus useful in the sense that it's clearer to dispense with the loss.
  \item It seems nice to point out and explore the fact that our notion of embedding is, now, symmetric.
    \begin{itemize}
    \item So generally we could say $L_1:\R_1\to\reals^\Y$ and $L_2:\R_2\to\reals^\Y$ are \emph{equivalent} (name TBD) if there exist $\Sc_i\subseteq\R_i$ representative for $L_i$, $i\in\{1,2\}$, with a bijection $\varphi:\Sc_1\to\Sc_2$ such that (i) for all $r\in\Sc_1$ we have $L_2(\varphi(r)) = L_1(r)$, and (ii) for all $p\in\simplex, r\in\R_1$ we have $r\in\prop{L_1}(p) \iff \varphi(r)\in\prop{L_2}(p)$.
    \item Now since $\varphi$ is a bijection it's clear that this is an equivalence relation.
    \item Moreover, since we've already established (Prop~\ref{prop:embed-bayes-risks}) that if $L$ embeds discrete $\ell$ over $\Sc$, then $\Sc$ being representative for $\ell$ implies $\varphi(\Sc)$ is representative for $L$, meaning $L$ and $\ell$ are equivalent under this definition.
    \item What other results might hold more generally using this equivalence notion?  (Note: finiteness of $\Sc$ is not assumed now, though we could make that assumption.)
    \item I believe the Bayes risk matching result may hold: $L_1$ and $L_2$ are equivalent iff $\risk{L_1}=\risk{L_2}$.  Certainly the first direction (equivalent $\implies$ risk matching) goes through untouched.  For the converse, I think we need finiteness of $\trim$, or maybe more generally some condition about the differentiability of the risk, since we needed the uniqueness of the supporting hyperplane to $\risk{L}$ to deduce that the losses matched.  Otherwise, if the Bayes risk has a nondifferentiable point, and the the level set of $u$ is that point, and $u$ is not redundant, there will be multiple loss vectors at $u$ which achieve the same Bayes risk.
    \end{itemize}
  \end{itemize}}

While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
\begin{definition}\label{def:prop-embed}
	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ on a set $\Sc$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
	If there is a representative set $\Sc$ such that $\Gamma$ embeds $\gamma$ on $\Sc$, then we simply say $\Gamma$ embeds $\gamma$.
	Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.
\end{definition}

>>>>

\begin{definition}
  \raft{For Bo: added this def, changed def embedding}
  Let $L:\R\to\reals^\Y_+$ be a generic loss.
  We say $\Sc \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
  We further say $\Sc$ is a \emph{minimum representative set}\jessiet{Propogate change} if it has the smallest cardinality among all representative sets.
\end{definition}

\begin{definition}[Embedding a loss]\label{def:loss-embed}
  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ \emph{over a set} $\Sc$ if there exists some injective embedding $\varphi:\Sc\to\reals^d$ such that
  (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
  % \begin{equation}\label{eq:embed-loss}
  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
  % \end{equation}
  \begin{equation}\label{eq:embed-loss}
    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
  \end{equation}
  We simply say $L$ \emph{embeds} $\ell$ if there is some representative set $\Sc$ for $\ell$ such that $L$ embeds $\ell$ over $\Sc$.
\end{definition}

@@

\raf{Some thoughts on this section:
  \begin{itemize}
  \item It's unclear to me how much of the properties stuff is for funzies versus useful in the sense that it's clearer to dispense with the loss.
  \item It seems nice to point out and explore the fact that our notion of embedding is, now, symmetric.
    \begin{itemize}
    \item So generally we could say $L_1:\R_1\to\reals^\Y$ and $L_2:\R_2\to\reals^\Y$ are \emph{equivalent} (name TBD) if there exist $\Sc_i\subseteq\R_i$ representative for $L_i$, $i\in\{1,2\}$, with a bijection $\varphi:\Sc_1\to\Sc_2$ such that (i) for all $r\in\Sc_1$ we have $L_2(\varphi(r)) = L_1(r)$, and (ii) for all $p\in\simplex, r\in\R_1$ we have $r\in\prop{L_1}(p) \iff \varphi(r)\in\prop{L_2}(p)$.
    \item Now since $\varphi$ is a bijection it's clear that this is an equivalence relation.
    \item Moreover, since we've already established (Prop~\ref{prop:embed-bayes-risks}) that if $L$ embeds discrete $\ell$ over $\Sc$, then $\Sc$ being representative for $\ell$ implies $\varphi(\Sc)$ is representative for $L$, meaning $L$ and $\ell$ are equivalent under this definition.
    \item What other results might hold more generally using this equivalence notion?  (Note: finiteness of $\Sc$ is not assumed now, though we could make that assumption.)
    \item I believe the Bayes risk matching result may hold: $L_1$ and $L_2$ are equivalent iff $\risk{L_1}=\risk{L_2}$.  Certainly the first direction (equivalent $\implies$ risk matching) goes through untouched.  For the converse, I think we need finiteness of $\trim$, or maybe more generally some condition about the differentiability of the risk, since we needed the uniqueness of the supporting hyperplane to $\risk{L}$ to deduce that the losses matched.  Otherwise, if the Bayes risk has a nondifferentiable point, and the the level set of $u$ is that point, and $u$ is not redundant, there will be multiple loss vectors at $u$ which achieve the same Bayes risk.
    \end{itemize}
  \end{itemize}}
\jessie{Thinking about this: I think there is enough value to $\trim$ as an object to include it.  The concept makes a lot more intuitive sense if we defined it by $\trim_\Sc(\gamma) = \{\gamma_r : r \in \Sc\}$ and thinking about the importance of $\Sc$.
There are a few results that are well-explained by this:
\begin{itemize}
	\item $L$ embeds discrete $\ell$ over set $\Sc$ (minimally representative for $\ell$) iff $\trim_\Sc(\prop{\ell}) = \trim_{\varphi(\Sc)}(\prop{L})$
	\item $L$ is equivalent to discrete $\ell$ iff $\trim_{\R_1}(\prop{\ell}) = \trim_{\R_2}(\prop{L})$
	\item when is $\ell$ non-redundant? (no reports $r$ s.t. $\gamma_r$ is (a) empty, (b) not a strict subset of another level set, or (c) exactly equal to another level set.)
	\item can't have reports that are strict subsets and on a facet of the epigraph <-- less clear how this would follow in this section.
\end{itemize}
This begs the question: what is the utility of non-redundancy?  It feels like getting rid of redundant reports makes it easier to study the property, where they don't really hurt much when studying the loss.}

While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another. \jessie{Merge with earlier definitions if we keep this section}
\begin{definition}\label{def:prop-embed}
	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ on a set $\Sc$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
	If there is a representative set $\Sc$ such that $\Gamma$ embeds $\gamma$ on $\Sc$, then we simply say $\Gamma$ embeds $\gamma$.
	Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.
\end{definition}
